---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- build with rmarkdown::render("README.Rmd") -->

```{r setup, include = FALSE}
set.seed(2018)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# s3vec

The goal of s3vec is to provide a wrapper around collections of s3 objects (of the same class) to make them behave like vectors of objects.

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://img.shields.io/badge/lifecycle-experimental-orange.svg)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/nbenn/s3vec?branch=master&svg=true)](https://ci.appveyor.com/project/nbenn/s3vec)
[![Travis build status](https://travis-ci.org/nbenn/s3vec.svg?branch=master)](https://travis-ci.org/nbenn/s3vec)
[![Coverage status](https://codecov.io/gh/nbenn/s3vec/branch/master/graph/badge.svg)](https://codecov.io/github/nbenn/s3vec?branch=master)

## Installation

You can install s3vec from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("nbenn/s3vec")
```

## Hello World

Assume we have an s3 class `point`, representing a point in 2 dimensions. Now we create 100 instances of `point` and store them in the list `points`.

```{r point}
point <- function(x, y) {
  stopifnot(is.numeric(x), is.numeric(y))
  structure(list(x = x, y = y), class = "point")
}

points <- mapply(point, runif(100L), runif(100L), SIMPLIFY = FALSE)
```

We would like to implement a `max` function that returns the point with the greatest distance from the origin. We cannot use s3 dispatch on `point`, because our collection of points is a list. For a function like `abs`, this is less of an issue, as it can be applied to individual objects by iterating through the list. 

```{r funcs, error = TRUE}
abs.point <- function(x) {
  sqrt(x$x ^ 2L + x$y ^ 2L)
}

abs(points[[1L]])
sapply(points[1:5], abs)

max.point <- function(x, ...) {
  max(sapply(x, abs))
}

max(points)
```

In order to get around this issue, `s3vec` wraps an additional class (`s3vec`) around such a list, holding several objects of the same type and bring this type to the surface of this wrapped object. Like this, s3 dispatch can be used for the point class.

```{r s3vec}
library(s3vec)

points <- as.s3vec(points)

class(points)

max(points)
```

Of course, in a simple scenario like this, one could argue that it makes more sense to use the point class as

```{r point-vec}
points <- point(runif(5L), runif(5L))
max(points)
```

In which case, this enclosing class is not necessary. But a solution like this becomes more involved when for example there is structural variation among class instances (e.g. a mix of 2D and 3D points).

```{r point-lst}
point <- function(coords) {
  stopifnot(is.numeric(coords))
  structure(coords, class = "point")
}

points <- replicate(10L, point(runif(sample(2:3, 1L))), simplify = FALSE)
sapply(points, length)
```

A completely vectorized approach as above is not as simple anymore and a list-based implementation might be better suited, in turn causing the problem described in the beginning.
